Robotic Cart System

### 2021-04-06 parts/03-acknowledgements.tex
Updated acknowledgements page

    \par Special Thanks to Andrew Fandel, Anthony Birge, and Dr. Suruz Miah for their work with Machine Learning on a 2-DOF Helicopter.
    \par Thanks to Mr. Christopher Mattus for his assistance in setting up our lab environment.
    \par Thank you to everyone else who helped make this project possible and sucessful.

>>>>

    \par Special thanks to Mr. Christopher Mattus for his assistance in procuring the parts and modifying the hardware for our project.
    \par Thank you to everyone else who helped make this project possible and successful.
